\subsection{Assessment}
\begin{enumerate}
\item Ask supervisee to describe the importance of enlisting the help of direct and indirect consumers.
\item Use behavior skill tracking to teach and practice describing interventions in nontechnical terms.
\item Discuss challenges in dealing with colleagues within different fields and strategies to help.
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Have supervisee identify ways they can build a rapport with other service providers and help support them when they have a student who needs to generalize and maintain skills in new settings.
\item Have supervisee choose a particular behavior change program or strategy. Have him/her describe and explain this program to an individual who does not have a background in applied behavior analysis. 
\item Have supervisee choose a specific behavior change program. Have him/her practice explaining the benefits of this program to others in order to get them on board with implementing this program.
\item Give supervisee a complex behavior change program. Have him/her simplify this program and create guidelines and instructions that they could give to an individual who does not have knowledge of applied behavior analytic strategies and techniques. 
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Ask supervisee to describe why it is important to provide supervision of behavior change agents.
\item Look at data with supervisee and ask them to discuss what modification they may consider
\item Have supervisee observe intervention in the home environment and ask them to write down suggestions to increase the effectiveness of the plan.
%
\end{enumerate}
%
