\subsection{Examples}
\begin{enumerate}
\item Accuracy: You and a friend decide to go on a 5-mile run.  Your friend tells you that she can monitor the distance because her legs always start to hurt once she runs 5 miles.  You, being a data-driven behavior analyst, decide that your friend's measurement procedure might not be the most accurate so you use your smart phone app to track the distance.  Your measurement system will likely reveal a better estimate of the true value of the distance you ran.
\item Reliability: Using the example for accuracy, both measures can be reliable if at the end of the run your friend tells you that you must have run 5 miles because her legs hurt and your app indicates you ran 5 miles.   
\end{enumerate}
%
\subsection{Examples}
\begin{enumerate}
\item John is conducting a functional analysis (FA) on aggression in one of his students. He has asked Mary to observe the behavior and record data simultaneously with him to calculate Interobserver agreement. He plans on conducting a 5-minute session with 30, 10-second intervals. He plans to use interval agreement IOA.  He records 4 instances of aggression during the FA in the 21st, 22nd, 23rd and 24th interval. Mary records 4 instances in the 21st, 22nd, 23rd, and 25th interval. He calculates IOA to be 97\% or 29/30 intervals.
\item (Non-example) John is conducting a functional analysis on aggression in one of his students. He asks Mary to come in and observe but does not provide her with a data recording sheet to take data on the behavior. At the end of the session he asks Mary if she saw any aggression during the session. 
\end{enumerate}
%
