\clearpage \section{\foureTwelve{}}
\subsection{Definition}
Errorless learning - an ``approach whereby the task is manipulated to eliminate/reduce errors. Tasks are executed in such a way that the subject is unlikely to make errors'' (Fillingham, Hodgson, Sage, \& Ralph, 2003, p. 339). 

Errorless learning techniques include most-to-least prompt fading or stimulus shaping/fading techniques. Prompts are removed gradually as the individual becomes more adept with the skill, thereby reducing the likelihood of errors.  To apply errorless learning, behavioral strategies utilized may include: response prevention (e.g. only S+ is presented allowing for only correct responding or physical guidance is provided with instruction so incorrect responses are not possible); verbal prompt fading; modeling; stimulus fading (e.g. emphasizing a physical dimension of the stimuli to evoke a correct response such as by illuminating the correct selection, S+, and presenting the incorrect selection, S-, in a dimmer format); or stimulus shaping (e.g. increasing likelihood of correct responding by gradually changing the shape of the stimulus to maintain correct responding). 

The advantages of errorless learning include that it removes negative side effects involved with trial-and-error learning and that it is proven particularly effective among individuals that suffer from brain damage or have a developmental disorder. The disadvantages include cost, time-intensity, and maybe considered less natural than trial-and-error learning (Mueller, Palkovic \& Maynard, 2007).

Trial-and-error learning, being presented with stimuli in which both the correct selection (S+) and incorrect selection (S-) are available, can lead to adverse side effects due to the possibility of incorrect responding and failure to access reinforcers. Research has shown that this can result in aggression, negative emotional responses and stimulus overselectivity (Mueller et al., 2007).
%
\subsection{Assessment}
\begin{enumerate}
\item Have supervisee demonstrate the difference between trial-and-error learning and errorless learning on the job or during role-play.
\item Have supervisee describe how and when prompts will be faded to promote independent responding. 
%
\end{enumerate}
%
\subsection{Relevant Literature}
\begin{refsection}
\nocite{fillingham2003application,
        mueller2007errorless,
        terrace1963errorless}
\printbibliography[heading=none]
\end{refsection}
%
\subsection{Related Tasks} 
\fourdThree{}\\
\fourdFour{}\\
\fourFKTwentyFour{}\\
