\clearpage \section{\fourFKTwentyOne{}}
\subsection{Definition}
Schedule of reinforcement/punishment – ``rule that specifies the environmental arrangements and response requirements that will result in reinforcement or punishment'' (Cooper, Heron \& Heward, 2007, p. 703).

Related Definitions:\\

A continuous schedule of reinforcement: reinforcement is given for each occurrence of behavior (also known as a 1:1 schedule of reinforcement or CRF).

A continuous schedule of punishment: punishment is given after each occurrence of behavior (also known as 1:1 schedule of punishment).
 
An intermittent schedule of reinforcement: reinforcement is given after some, but not all occurrences of behavior.

\subsection{Examples}
Types of intermittent schedules of reinforcement are listed with examples below.
\begin{enumerate}
\item A fixed ratio schedule of reinforcement: Requires a completion of a specified number of responses to gain access to reinforcement. Example: A student may have to complete 5 correct math problems on a computer game before progressing to the next level (this is a FR-5 schedule of reinforcement).
\item A variable ratio schedule of reinforcement: Requires the completion of a varied number of responses to gain access to reinforcement. Example: A young girl may be called on when she raises her hand quietly in class on average once every 5 times. Sometimes, the teacher calls on her every 4 times she raises her hand. Other times the teacher calls on her every 6 times she raises her hand. The teacher provides attention on average every 5 times (this is a VR-5 schedule of reinforcement).
\item A fixed interval schedule of reinforcement: provides reinforcement for the first response after a fixed duration of time. Example: An alarm clock is set for 7:00 am every morning. If an individual presses snooze, it will allow the individual to sleep in again for 10 minutes. The individual cannot press snooze before the alarm rings (this is a FI-10 minute schedule of reinforcement).
\item A variable interval schedule of reinforcement: produces reinforcement for the first response after a variable duration of time. Example: A person goes to a fast food restaurant. Sometimes he has to stand in line, while other times, he may order immediately upon entering. This interval varies each time he goes to the restaurant. 
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item During a job or during role-play, have your supervisee determine what schedule of reinforcement or punishment is being used
\item Use SAFMEDS or flashcards to practice definitions related to the various types of schedules.
%
\end{enumerate}
%
\subsection{Relevant Literature}
\begin{refsection}
\nocite{cooper2007applied}
\printbibliography[heading=none]
\end{refsection}
%
\subsection{Related Tasks} 
\fourdTwo{}\\
\fourdSeventeen{}\\
