\subsection{Assessment} 
\begin{enumerate}
\item Ask your supervisee to identify the frequency of hand raising above.
\item Ask your supervisee to create another example and non-example of his/her own.
\item Have supervisee measure a frequency of a behavior on the job or in a role play.
\item Have supervisee graph the frequency measured on the job or in a role play.
\end{enumerate}
%
\subsection{Assessment} 
\begin{enumerate}
\item Ask your supervisee to identify the frequency of chip eating or basketball dribbles in examples.
\item Have supervisee measure a frequency of a behavior on the job or in a role play.
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Provide hypothetical situations and ask your supervisee if using percent of occurrence measures are appropriate
\item Provide various hypothetical situations and ask your supervisee to calculate percent of occurrence
\item Have supervisee graph percent of occurrence measured on the job or in a role play
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Ask Supervisee to measure their own duration related to a task (eg. give them a timer and crossword puzzle to complete)
\item Ask Supervisee to measure and calculate the rate of someone tapping their pen (or another discrete behavior) during a 10 minute meeting
\item Ask Supervisee to observe a conversation between colleagues and measure latency regarding question asking-answering.  Have Supervisee use a timer/stop watch to record latency
\item Ask Supervisee to record their own latency during a supervision meeting when asked to define a task list item, vs. a concept 
\item Ask Supervisee to measure interresponse time (IRT) by observing someone eating a meal for 5 minutes; have Supervisee record time between swallowing one bit of food and next bite and report the average IRT.
%
\end{enumerate}
%
