\clearpage \section[\fourgFour{}]{\fourgFour{}%
              \sectionmark{G-04 Explain behavioral concepts...}}
\sectionmark{G-04 Explain behavioral concepts...}
\subsection{Definition}
It is important for a behavior analyst to have a strong verbal repertoire when speaking about the science of behavior analysis. Jargon used in journals, universities, and with other behavior analysts is valuable to promote effective action on the part of the listener with precise discriminative control. 

That being said, Skinner wrote that we should choose words for the effects they have on the listener (Skinner, 1957) and unless that listener has extensive training in behavior analysis, our use of technical language will ``fall on deaf ears'' and not produce effective action. When speaking with client family members, friends, or professionals from other closely related fields, it is important to remember that your verbal behavior is for the benefit of your audience. Bailey (1991) describes this phenomenon well:

``In our zeal to be scientific, we have stressed the need to match the requirements of science in our writing and publishing. Although this has given us much-needed academic credibility (faculty can be promoted and tenured by publishing in JABA) it doesn't help at all in selling our technology to the masses'' (p. 446)

During the supervision process, spend considerable amounts of time, working on precise definitions for technical terms. This benefits the supervisee in several ways. It allows him/her to behave effectively as a listener and speaker when interacting with other behavior analysts in the field. It will also promote accurate translations to nontechnical language. If a precise definition is practiced, a less technical, more layperson-friendly definition will be easier to describe and it will be more likely to be accurate.
%
\subsection{Assessment}
\begin{enumerate}
\item Ask Supervisee to give a precise definition of a behavioral term from a textbook. Then ask Supervisee to accurately describe the term in nontechnical language. Work on this for the most commonly used terms. Provide feedback after, when in a supervision meeting.
\item Observe the Supervisee describing a behavior analytic concept to another person (client, colleague, etc.) The Supervisee should be able to answer basic questions related to the topic using nontechnical language. Provide feedback after, when in a supervision meeting.
\end{enumerate}
%
\subsection{Relevant Literature}
\begin{refsection}
\nocite{bailey1991marketing,
        lindsley1991technical,
        malott1992should}
\printbibliography[heading=none]
\end{refsection}
\subsection{Related Tasks}
\fourgSix{}\\
\fouriSix{}\\
\fourjSix{}\\
\fourjSeven{}\\
\fourkOne{}\\
\fourkThree{}\\
\fourkEight{}\\
\fourkNine{}\\
