\clearpage \section[\fourkTen{}]{\fourkTen{}%
              \sectionmark{K-10 Arrange for... termination}}
\sectionmark{K-10 Arrange for... termination}
\subsection{Definition}
Behavior analysts follow guidelines related to arranging for termination of services in 2.15 of the Behavior Analyst Certification Board professional and ethical compliance code for behavior analysts:

2.15 Interrupting or Discontinuing Services. \\
 (d) Discontinuation only occurs after efforts to transition have been made. Behavior analysts discontinue a professional relationship in a timely manner when the client: (1) no longer needs the service, (2) is not benefiting from the service, (3) is being harmed by continued service, or (4) when the client requests discontinuation. \\
(e) Behavior analysts do not abandon clients. Prior to discontinuation, for whatever reason, behavior analysts: discuss the client's views and needs, provide appropriate pre-termination services, suggest alternative service providers as appropriate, and take other reasonable steps to facilitate timely transfer of responsibility to another provider if the client needs one immediately, upon client consent. (BACB, 2014, P. 10).

Before services are terminated, behavior analysts must discuss the client's needs with all pertinent parties (e.g. client's parents, legal guardians, school administrators). The client's welfare should be prioritized above all else and a transition plan should be put in place well before services are discontinued. Referrals to other professionals should be given if appropriate. (Bailey \& Burch, 2005)
%
\subsection{Assessment}
\begin{enumerate}
\item Ask supervisee to describe conditions under which services should be discontinued for a client
\item Ask supervisee what steps they should undergo before discontinuing a client's services
%
\end{enumerate}
%
\subsection{Relevant Literature}
\begin{refsection}
\nocite{bailey2013ethics,
        bac2014professional}
\printbibliography[heading=none]
\end{refsection}
%
\subsection{Related Tasks}
\fourgSeven{}\\
\fourkNine{}\\
