\subsection{Assessment}
\begin{enumerate}
\item Have supervisee list and describe each measurable unit of behavior.
\item Have supervisee list and describe each of the three fundamental properties of behavior.
\item Provide the supervisee with a number of scenarios. Have the supervisee design/describe a data collection procedure to measure target behavior.
%
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Ask the supervisee to describe situations that would be appropriate to use event recording procedures. 
\item Ask the supervisee to describe situations that may not be appropriate to use an event recording procedure.
\item Ask the supervisee to use an event recording procedure to measure 3 responses at one time. Ask the student to design a datasheet and method for counting that will help the observer record the responses accurately. 
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Ask your Supervisee to describe each of the 3 types of time sampling methods listed above.
\item Have your Supervisee practice each type of data collection method in his/her job role or through role-playing.
\item Ask them to tell you which time sampling method is being employed in each of the following examples:
\item An observer is interested in a client's interactions with his/her peers. They observe him/her across a 10-minute period; at the end of each 10-second interval, they record the behavior as being present if the client has had any interaction with his/her peers at all during the interval. (Answer = Partial-interval recording).
\item An observer is examining a client's on-task behavior in class. They observe him/her for a 60-minute period and divide the hour up into 5-minute intervals. If the client is on-task at the end of the 5-minute interval, on-task behavior is scored as having been observed. (Answer = Momentary time sampling). 
\item A client's humming behavior is being observed; the observer divides a 15-minute observation time up into 30-second intervals. If humming was observed throughout the entire 30-second interval, the behavior is scored as having occurred in that interval. (Answer = Whole-interval recording). 
\end{enumerate}
%
