\subsection{Examples}
\begin{enumerate}
\item A teacher is asked to record the number of times a student yells out inappropriate language in class each day. Since the time the student spends in class varies widely during the week, the behavior analyst designed a measurement system to record rate (number of occurrences divided by time in class) of yelling out inappropriate language. With these data, the behavior analyst can compare the student's behavior across time of unequal durations. 
\item A parent is committed to accurately recording data to show duration of a child's tantrums, but found that she was not always in close proximity with the child when the behavior begins. The behavior analyst identifies two conditions during the day when the mother can accurately record duration of each tantrum (the first 30 minutes after school and the last 30 minutes before bedtime). The mother records duration of total tantruming behavior during each 30 mimute-observation twice a day.
\end{enumerate}
%
\subsection{Examples}
Examples of contexts that are likely to be appropriate for an event recording procedure:
\begin{enumerate}
\item Property destruction that typically occurs two to five times a week. 
\item Correct responses to the question, ``What do you want?'' when asked in at least six distributed trials each day. 
\end{enumerate}
Examples of contexts that may be inappropriate for an event recording procedure: 
\begin{enumerate}
\item Vocal Stereotypy that occurs on and off so rapidly that an observer would not be able to accurately determine the start and end of the stereotypy.
\item Aggressive behavior in a classroom setting with one teacher, who must conduct instruction, interact with other students, and count hitting behavior that often includes multiple students.  
\item An observer may increase counting accuracy by using a counting device with low-technology (i.e., masking tape around the wrist for tally marks or a golf-stroke counter or with high technology (i.e., iPad or laptop direct observation programs). 
\end{enumerate}
%
\subsection{Examples}
Whole-Interval Recording
\begin{enumerate}
\item Student moves one or both hands repeatedly and rapidly by bending at the wrist, such that fingers move more than 2 inches. 
\item (Non-example) Waving hand to say ``hello'' or ``goodbye.''
\item An observer divides a 5-minute observation period into intervals of 5 seconds. A student flaps his hands for the entire 5-second interval. At the end of the 5-second interval, the observer records the behavior as having occurred.
\end{enumerate}
%
Partial-Interval Recording\\
Student displays \textit{palilalia}, or repeating a word, phrase, or sentence with no direct, observable relationship with the immediate environment. An observer divides a 5-minute observation period up into intervals of 10 seconds. A student emits palilalia for the entire 10-second interval. At the end of the 10-second interval, the observer records the behavior as having occurred.
\begin{enumerate}
\item Calling-out behavior in a pupil: student raises voice above conversation level when not called on by teacher.
\item A 30-minute observation period is divided into one-minute intervals.  At the end of the one minute interval, the behavior is recorded as having occurred because the pupil called-out after the first 30 seconds of the interval.
\item A child touches or manipulates toys. A 5-minute observation period is divided up into 10-second intervals. The observer records the behavior as having occurred in the last 10-second interval because the child had engaged with the toy at some point during the interval. 
\end{enumerate}

Momentary Time Sampling\\
\begin{enumerate}
\item Movie watching: client is seated, and head and eyes are oriented toward screen.
\item An observer is measuring a client's engagement with a movie across a 2-minute period. The 2-minute period is divided up into 5-second intervals. The observer records the behavior as being present at the end of the first 5-second interval as the client was watching the movie appropriately at that specific point in time. 
\end{enumerate}
%
