\subsection{Assessment}
\begin{enumerate}
\item Have supervisee create a list of unconditioned reinforcers. Have him/her define and describe the role satiation and deprivation plays in unconditioned reinforcement. 
\item Have supervisee give examples of unconditioned reinforcers. Have him/her describe the difference between conditioned and unconditioned reinforcement.
\item Have supervisee explain the relationship between conditioned and unconditioned reinforcers and the role unconditioned reinforcers may play in creating conditioned reinforcers.
\end{enumerate}
%
\begin{enumerate}
\item Have supervisee explain the differences between conditioned and unconditioned reinforcers.
\item Have supervisee explain the process of producing a conditioned reinforcer (i.e., token systems). Have him/her give an example from their professional experience.
\item Have supervisee read and summarize a journal article on the topic of conditioned reinforcement. 
\end{enumerate}
%
\begin{enumerate}
\item Ask your supervisee to explain contingency shaped behavior 
\item Ask your supervisee how contingency shaped is different from rule-governed behavior
\item Ask your supervisee to create another example and non-example of his/her own. 
\item Ask your supervisee to state why it might be better to use contingency shaped consequences as opposed consequences, which are more delayed or rule governed      
\end{enumerate}
%
\begin{enumerate}
\item Have supervisee give examples of Premack's principle in his/her daily life.
\item Have supervisee create a role play scenario in which he/she demonstrates the use of the Premack principle.
\item Have supervisee find an article on the use of the Premack principle, summarize, and discuss benefits and limitations of use.
\end{enumerate}
%
