\subsection{Examples}
\begin{enumerate}
\item Food, water, oxygen, warmth, and sexual stimulation are some examples of unconditioned reinforcers.
\item A teacher gives a child a pretzel after the child does a task. The child's engagement in the task increases in the future. 
\item This is an example of unconditioned reinforcement.
\end{enumerate}
%
%\subsection{Examples}
\begin{enumerate}
\item  Money, tokens, stickers.
\item A teacher says ``good job'' after a student returns their homework. The student continues to return their homework in the future. 
%
\end{enumerate}
%
%\subsection{Examples}
\begin{enumerate}
\item Melvin puts a dollar into the soda machine and pushes the cola button. Seconds later a can of soda comes out. He opens the soda and drinks it.  He buys 3 more drinks from the same machine that week.
\item Simon's friend Ernest is a prankster.  Ernest shakes up a can of soda and offers Simon a drink.  The can sprays him in the face and soaks his clothing.  The next time Ernest offers a soda, Simon is hesitant to accept.  Although he'd like to open the soda and drink it, he hands it back expecting another explosive surprise.
\item Thirsty Floyd finds a 12 pack of old sodas in the storeroom.  He cracks a can and starts to drink. Unfortunately, the soda has gone bad. Floyd gets sick from drinking the soda. In the future Floyd avoids drinking old sodas.
\item (Non-example) Horace's mom tells him that drinking soda is bad for him. Horace avoids drinking soda in the future.
\end{enumerate}
%
\begin{enumerate}
\item A father tells his teenage son, ``When you have finished washing the dishes, you can watch TV.''
\end{enumerate}
%
