%\clearpage \section{\fourFKTen{}}
\subsection{Definition}  
Behavior - ``The activity of living organisms; human behavior includes everything that people do'' (Cooper, Heron, \& Heward, 2007, p. 25).

Response - A single instance or occurrence of a specific class or type of behavior'' (Cooper, Heron, \& Heward, 2007, p. 703).  

Response Class - ``A group of responses of varying topography, all of which produce the same effect on the environment'' (Cooper, Heron, \& Heward, 2007, p. 703).  
%
\subsection{Examples}
Opening a door
\begin{enumerate}
\item Example (behavior):  Beezus stands up from her chair, heads towards a closed door, and pushes on it.  The door is now open.  
\item Example (response): When encountering a closed door, Beezus extends an open palm and pushes on it.  The door is now open.   
\item Example (response class): Beezus encounters many doors during her day. Sometimes she opens them with an open palm and sometimes with a closed palm. Some times she opens them with her left hand and at other times with her right hand.  No matter which way she chooses to open a door, the result is always the same.  
%
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Ask your supervisee to define behavior, response, and response class. 
\item Ask your supervisee to identify the behavior(s), responses, and response class from the above examples.  
\item Ask your supervisee to create other examples and non-examples of his/her own. 
\item Have your supervisee describe how these three terms are related. 
%
\end{enumerate}
%
\subsection{Relevant Literature}
\begin{refsection}
\nocite{cooper2007applied,
        johnston1993strategies,
        michael2004concepts,
        skinner1969contingencies}
\printbibliography[heading=none]
\end{refsection}
%
\subsection{Related Tasks}
\fourFKThirtySix{}\\
\fourgFive{}\\
\fouriOne{}\\
