\subsection{Assessment}
\begin{enumerate}
\item Ask the supervisee to name the basic unit of language
\item Ask the supervisee to name all 6 of the elementary verbal operants
\item Ask the supervisee to name some of the standardized tests often used to assess language
\item Ask the supervisee to explain why these standardized tests may not provide adequate information
\item Ask the supervisee to describe how one might assess an individual's use of verbal operants if testing fails to yield enough information.
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Ask the supervisee to state what echoic training can be used to teach.
\item Ask the supervisee to give examples of echoic training.
\item Ask the supervisee to discuss how echoic training should be delivered.
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Ask the supervisee to state what mand training can be used to teach.
\item Ask the supervisee to give examples of mand training.
\item Ask the supervisee to state why it is important to fade the non-verbal stimulus and the echoic prompt.  
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Ask the supervisee to state what tact training can be used to teach.
\item Ask the supervisee to give examples of tact training.
\item Ask the supervisee to discuss how tact training should be delivered.
\item Ask the supervisee to state how the verbal model can be successfully faded out.
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Ask the supervisee to state what intraverbal training can be used to teach.
\item Ask the supervisee to state the prerequisite skills that are needed to teach intraverbal behavior.  
\item Ask the supervisee to give examples of intraverbal training.
\item Ask the supervisee to discuss how intraverbal training should be delivered.
\item Ask the supervisee to state why nonverbal stimuli should be faded out.
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Have supervisee read relevant literature on receptive language/listener training.
\item Role play with your supervisee teacher (speaker) and student (listener) examples of receptive language training protocols.
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Ask the supervisee to give the definition of an echoic
\item Ask the supervisee to give several examples of echoics
\item Ask the supervisee to give a non-example of an echoic 
%
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Ask your Supervisee to recall how they asked for supervision
\item Ask your Supervisee to list the types of mands they would emit if they were lost in a foreign county and needed directions to a local gas station
\item Ask you supervisee to list 5 ways they use mands in an inappropriate way (eg. complain about work to get attention)
%
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Ask the supervisee to define ``tact.''  
\item Ask the supervisee to give several examples of tacts.
\item Ask the supervisee to give a non-example of a tact. Discuss why.
%
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Ask the supervisee to define ``intraverbal''  
\item Ask the supervisee to give several examples of intraverbals.
\item Ask the supervisee to give a non-example of an intraverbal.
%
\end{enumerate}
%
