\subsection{Assessment}
\begin{enumerate}
\item Ask your supervisee to identify the duration of furniture assembly from the example above
\item Ask your supervisee to create another example and non-example of his/her own
\item Have your supervisee measure the duration of another behavior on the job or in role-play.
\item Have the supervisee graph the duration of another behavior measured on the job or in a role-play.
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Ask your supervisee to identify the latency of a few responses of your choosing.  
\item Ask your supervisee to create another example and non-example of his/her own.
\item Have your supervisee measure the latency to another behavior on the job or in role-play.
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Ask your supervisee to identify the interresponse time in the examples above. 
\item Ask your supervisee to create another example and non-example of his/her own. 
\item Have your supervisee measure the interresponse time of a behavior on the job or in a role-play. 
\item Have your supervisee graph the interresponse time measured on the job or in a role-play.
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Ask Supervisee to measure their own duration related to a task (eg. give them a timer and crossword puzzle to complete)
\item Ask Supervisee to measure and calculate the rate of someone tapping their pen (or another discrete behavior) during a 10 minute meeting
\item Ask Supervisee to observe a conversation between colleagues and measure latency regarding question asking-answering.  Have Supervisee use a timer/stop watch to record latency
\item Ask Supervisee to record their own latency during a supervision meeting when asked to define a task list item, vs. a concept 
\item Ask Supervisee to measure interresponse time (IRT) by observing someone eating a meal for 5 minutes; have Supervisee record time between swallowing one bit of food and next bite and report the average IRT.
%
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Have the supervisee read the Fahmie \& Hanley (2008) article. Then provide the supervisee with examples of different data analysis units along the continuum the authors display in Figure 1. Have them place the scenarios along the continuum and discuss. 
\item Have the supervisee describe different methods of within session data collection ( e.g. minute-by-minute, event based observation period comparisons) and their utility ( a review of the methods used in the relevant literature will assist with this task)
%
\end{enumerate}
%
