\subsection{Examples}
\begin{enumerate}
\item Sarah gets a fancy new piece of furniture from one of those Swedish companies.  When it arrives, Sarah realizes that it is not assembled.  She reads the complicated set of directions and begins putting it together at 2:12pm. Armed with a screwdriver and an Allen wrench, she consistently works to put it together until 3:43pm. Phew! Maybe next time she will order the one that comes fully assembled! The duration of the project was 1 hour and 31 minutes.
\item Benny gets a new yo-yo for his birthday and plays with it for 20 minutes after eating his cake and ice cream. He puts it down to play tag with his sister. The duration of yo-yo playing is 20 minutes.
\end{enumerate}
%
\subsection{Examples}
\begin{enumerate}
\item Hitting the snooze button or hitting the break
\item Example: Gertrude is not a morning person.  Her alarm goes off at precisely 5:30AM.  She hears the annoying wail but doesn't respond immediately.  After 32 seconds of beeping, she whacks the snooze button, rolls over and goes back to sleep.  Latency to turning off the alarm is 32 seconds.
\item Example:  Marty is driving down a country road.  Out of nowhere a herd of deer dart out in front of his car.  It takes Marty 5 seconds from the time he first sees the deer to hit the break.  Latency from the time the deer are spotted to applying pressure to the break is 5 seconds.    
\item Non-example: Gertrude is not a morning person.  Her alarm goes off at precisely 5:30 AM.  She does not respond to its annoying wailing and continues to sleep despite the noise.  The alarm stops on its own 1 hour later.
\end{enumerate}
%
\subsection{Examples} 
\begin{enumerate}
\item Sparky loves to bark at passing cars.  He hears a car drive by the house and barks.  Thirty-seven seconds later another car passes by and Sparky barks again.  Interresponse time between barking at the vehicles is thirty-seven seconds.
\item Doodles the cat likes to scratch the furniture.  She walks over the chair and sinks her claws in.  Eleven seconds later Doodles walks over to the couch and begins to scratch again.  Interresponse time between scratches is eleven seconds.  
\item Roger the rooster doesn't know that he's only supposed to crow at dawn. He lets out crows all day long.  He is observed to crow at 3:43 in the afternoon.  He crows again at 3: 59.  Interresponse time between crows is sixteen minutes.  
\item (Non-example) Sparky's owner accidentally steps on his tail.  Sparky yelps from the pain. 
\end{enumerate}
%
