\subsection{Assessment}
\begin{enumerate}
\item Ask supervisee to list considerations for the use of positive reinforcement.
\item Ask supervisee to list considerations for the use of negative reinforcement.
\item Have supervisee outline which considerations may affect a particular client and what behavioral strategies can be used to curb these unwanted effects.
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Ask the supervisee to state the unwanted effects of punishment.
\item Ask the supervisee to plan for unwanted effects of punishment.  The supervisor should provide examples of commonly used punishment procedures within agency (such as restraint, time outs, or other punitive measures) and ask the supervisee to propose solutions to these problems. 
\item Ask the supervisee to select one behavior to target for increase for each behavior targeted for decrease. 
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Ask your supervisee to list the possible unwanted effects of extinction.
\item Ask your supervisee in which situations should extinction not be utilized.
\item Ask your supervisee what behavioral strategies can mitigate the unwanted effects of extinction.
\item Have your supervisee determine which of his/her clients could benefit from extinction and which clients should avoid the use of extinction. 
%
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Ask your Supervisee to define behavioral contrast.
\item Ask your Supervisee to describe what will happen in this example if behavioral contrast is in effect: 
\item A child has been playing with two musical toys, allocating an equal amount of time playing with each toy. One of the musical toys is yellow and one of the musical toys is red. The red toy's battery begins to give out so that when the child presses the button, sometimes the music is not produced. However, the yellow musical toy continues to work well and music is produced each time the child pushes the button. What will happen to the rate of responding for each of the musical toys? (Answer = the rate of responding on the red musical toy will decrease and the rate of responding on the yellow toy will increase, even though there isn't any additional reinforcement being produced from the yellow toy).
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Have supervisee describe the principles of punishment and reinforcement and how behavioral contrast relates to each.
\item Have supervisee explain why rates may fluctuate based on punishment and reinforcement contingencies in multiple schedules.
\item Have supervisee give examples of behavioral contrast from their experiences and what they have done in those circumstances.
%
\end{enumerate}
%
