%
\subsection{Examples}
\begin{enumerate}
\item Cooper, Heron and Heward (2007) give a good example of behavioral contrast to illustrate the concept; ``...a pigeon pecks a backlit key, which alternates between blue and green, reinforcement is delivered on the same schedule on both keys, and the bird pecks at approximately the same rate regardless of the key's color'' (p. 337). However, this changes so that responses on one component of the schedule are punished, i.e., pecks on the blue key are punished because reinforcement is not delivered, but pecks on the other (green) key continue to produce reinforcement. As a result, rate of responding decreases on the blue key and rate of responding on the green key increases, even though no more reinforcement is delivered from the green key than before.
\end{enumerate}
%
Plan for the effects of behavioral contrast
\begin{enumerate}
\item It is important to consider prior to beginning an intervention, whether behavioral contrast may occur as a result of that planned intervention. If behavioral contrast is a possibility; then planning for its occurrence is crucial.
\item Cooper, Heron and Heward (2007, p. 338) suggest that one way to minimize or completely prevent the contrast effects of punishment is to plan the intervention so that the consequence is consistently applied to the target behavior across all relevant environments and stimulus conditions. All those involved in the client's life that may be required to deliver the consequence, will need to be thoroughly trained to ensure its consistent implementation.
\item Additionally, reinforcement will need to be minimized, or where possible, withheld, when the target behavior has occurred. Similarly, training will need to be provided to all those involved so that the client isn't receiving reinforcement when the target behavior is emitted.
\end{enumerate}
%
\subsection{Examples}
\begin{enumerate}
\item Rich sneaks candy from home and eats it in class. His teacher catches him one day and he stops eating candy in the classroom. However, he now asks to go to the bathroom every morning and eats candy in the bathroom where the teacher cannot see him. 
%
\end{enumerate}
%
