%\clearpage \section{\fourfOne{}}
\subsection{Definition}
Self-management - ``...behavior that a person emits to influence another behavior'' (Cooper, Heron, \& Heward, 2007, p. 577).

Skinner (1953) first outlined the idea of self-management with his theories on self-control. He defined self-control as, ``When a man controls himself, chooses a course of action, thinks out the solution to a problem, or strives towards an increase in self-knowledge, he is behaving. He controls himself precisely as he would control the behavior of anyone else- through the manipulation of variables of which behavior is a function'' (pp. 228-229).

``All self-control- or self-management- tactics can be operationalized in terms of two behaviors: (a) the target behavior a person wants to change (Skinner's controlled response) and (b) the self-management behavior (Skinner's controlling response) emitted to control the target behavior'' (Cooper et al., 2007, p. 577).

Applications include ``helping a person be more effective and efficient in his daily life, replacing bad habits with good ones, accomplishing difficult tasks, and achieving personal goals'' (Cooper et al., 2007, p. 579).
%
\subsection{Examples}
\begin{enumerate}
\item     • Skipping lunch (controlling behavior) to enjoy all three courses of your dinner (controlled behavior).
\item Leaving a bag of garbage near the front door (controlling behavior) to remind you to take it to the dumpster next time you leave the house (controlled behavior).
%
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Have supervisee identify and define a personal target behavior they would like to increase or decrease. (i.e., exercising more, eating less, studying more, swearing less, etc.). 
\item Have him/her research various self-management studies relevant to the target behavior they want to decrease. 
\item Have supervisee create guidelines and criteria for their self-management project to be reviewed by supervisor. 
\end{enumerate}
%
\subsection{Relevant Literature}
\begin{refsection}
\nocite{cooper2007applied,
        agran1997student,
        baum2005understanding,
        epstein1997skinner,
        kazdin2012behavior,
        skinner1953science,
        thoresen1974behavioral,
        watson2013self}
\printbibliography[heading=none]
\end{refsection}
%
\subsection{Related Lessons}
\fourbThree{}\\ 
\fourfTwo{}\\
\fouriOne{}\\
\fouriSix{}\\
\fourjOne{}\\
\fourjTwo{}\\
\fourjTen{}\\
\fourFKEighteen{}\\
\fourFKTwenty{}\\
\fourFKThirtyOne{}\\
