\clearpage \section{\fouraThree{}}
\subsection{Definition}
Duration – ``A measure of the total extent of time in which a behavior occurs'' (Cooper, Heron, \& Heward, 2007, p. 79).
%
\subsection{Examples}
\begin{enumerate}
\item Sarah gets a fancy new piece of furniture from one of those Swedish companies.  When it arrives, Sarah realizes that it is not assembled.  She reads the complicated set of directions and begins putting it together at 2:12pm. Armed with a screwdriver and an Allen wrench, she consistently works to put it together until 3:43pm. Phew! Maybe next time she will order the one that comes fully assembled! The duration of the project was 1 hour and 31 minutes.
\item Benny gets a new yo-yo for his birthday and plays with it for 20 minutes after eating his cake and ice cream. He puts it down to play tag with his sister. The duration of yo-yo playing is 20 minutes.
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Ask your supervisee to identify the duration of furniture assembly from the example above
\item Ask your supervisee to create another example and non-example of his/her own
\item Have your supervisee measure the duration of another behavior on the job or in role-play.
\item Have the supervisee graph the duration of another behavior measured on the job or in a role-play.
\end{enumerate}
%
\subsection{Relevant Literature}
\begin{refsection}
\nocite{cooper2007applied,deleon1999examination}
\printbibliography[heading=none]
\end{refsection}%


\subsection{Related Tasks}
\fourhOne{}\\
\fouriOne{}\\
\fourFKFourtySeven{}\\
