\subsection{Assessment}
\begin{enumerate}
\item Ask your Supervisees to define both positive and negative reinforcement and give an example of each type.
\item Ask your Supervisee to demonstrate an example of positive and negative reinforcement through role-playing.
\item Ask your Supervisee to identify which type of reinforcement is operating in these examples:
\begin{enumerate}
\item A Supervisee sees her BCBA Supervisor coming in to the classroom to run teaching evaluations. The Supervisee takes her client for a reinforcer break in another room and thereby avoids having a teaching evaluation completed on her. The next day, when her Supervisor comes back in to do more evaluations, she takes her client outside to play. (Answer = the Supervisee's behavior of leaving the classroom is negatively reinforced by avoiding having teaching evaluations completed on her).
\item A client regularly has challenging behavior when working with his teacher at the table, as he does not enjoy the work. However, on this occasion he has worked really well so has immediately been given a 3-minute break to run around in the playground. He continues to work well at the table after his break. (Answer = the client's hard work at the table may be being negatively reinforced. This is because his work behavior is being reinforced with removal from the table environment). 
\item A Father calls his son down to the dishes. His son comes down and does the dishes. His Father says ``Thanks, Son'' and gives him a dollar to get some candy. The next day when the son is asked to do the dishes again, he quickly comes down to do them. (Answer = the son's compliant behavior was probably positively reinforced with praise and/or money).
\end{enumerate}
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Provide the supervisee with articles from the relevant literature and discuss the findings and their considerations for clinical application. 
\item Ask the supervisee to list the problems associates with using extinction procedures alone 
\item Ask supervisee to list the benefits of using reinforcement based procedures with extinction
\item Ask the supervisee to list the problems associates with using punishment procedures alone
\item Ask supervisee to list the benefits of using reinforcement based procedures with punishment
\end{enumerate}
%
