\subsection{Assessment}
\begin{enumerate}
\item Provide scenarios in which clients would not qualify for a punishment procedure (e.g., behavior does not cause physical harm, reinforcement based strategies have not been attempted, or consent was not obtained.)
\item Ask Supervisee to list the four considerations the BACB lists when considering punishment
\item Ask the Supervisee to list the side effects of punishment
\item Ask the Supervisee to outline the recommendation for a client who had been receiving a punishment procedure for 2 months and head hitting remained consistent at 10 times a day. (should discontinue)
\item Have the supervisee list all of the things that must happen prior to a punishment procedure beginning (functional assessment, reinforcement based program ineffective, consent obtained, staff trained)
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Ask your supervisee to explain contingency shaped behavior 
\item Ask your supervisee how contingency shaped is different from rule-governed behavior
\item Ask your supervisee to create another example and non-example of his/her own. 
\item Ask your supervisee to state why it might be better to use contingency shaped consequences as opposed consequences, which are more delayed or rule governed      
\end{enumerate}
%
\begin{enumerate}
\item Ask the supervisee to describe an example of unconditioned punishment.
\item Use the supervisee to describe the difference between unconditioned punishment and an unconditioned punisher.
\item Ask the supervisee to list as many unconditioned punishers as possible in one minute.
\end{enumerate}
%
\begin{enumerate}
\item Ask supervisee to explain the process of conditioned punishment.
\item Ask supervisee to define a conditioned punisher.
\item Ask supervisee to provide examples of conditioned punishment and a conditioned punisher.
\item Ask supervisee to identify examples of conditioned punishment in a client's environment.
%
\end{enumerate}
%
\begin{enumerate}
\item Provide a hypothetical scenario and have your supervisee determine if an extinction procedure is in place. If so, have your supervisee define which type of extinction.
\item Have your supervisee give you 3 various examples of extinction. 
\item Describe the pros and cons of extinction procedures based on readings assigned.
\end{enumerate}
%
