\subsection{Assessment}
\begin{enumerate}
\item Ask supervisee to give examples of an unconditioned punisher
\item Ask supervisee to give examples of a conditioned  punisher
\item Ask supervisee to identify ethical considerations regarding the use of punishment and selecting punishers 
\item Ask supervisee to list the characteristics that should be considered when selecting a punisher 
\end{enumerate}
%
%\subsection{Assessment}
\begin{enumerate}
\item Have supervisee create a list of unconditioned reinforcers. Have him/her define and describe the role satiation and deprivation plays in unconditioned reinforcement. 
\item Have supervisee give examples of unconditioned reinforcers. Have him/her describe the difference between conditioned and unconditioned reinforcement.
\item Have supervisee explain the relationship between conditioned and unconditioned reinforcers and the role unconditioned reinforcers may play in creating conditioned reinforcers.
\end{enumerate}
%
\begin{enumerate}
\item Have supervisee explain the differences between conditioned and unconditioned reinforcers.
\item Have supervisee explain the process of producing a conditioned reinforcer (i.e., token systems). Have him/her give an example from their professional experience.
\item Have supervisee read and summarize a journal article on the topic of conditioned reinforcement. 
\end{enumerate}
%\subsection{Assessment}
\begin{enumerate}
\item Ask the supervisee to describe an example of unconditioned punishment.
\item Use the supervisee to describe the difference between unconditioned punishment and an unconditioned punisher.
\item Ask the supervisee to list as many unconditioned punishers as possible in one minute.
%
\end{enumerate}
%
%\subsection{Assessment}
\begin{enumerate}
\item Ask supervisee to explain the process of conditioned punishment.
\item Ask supervisee to define a conditioned punisher.
\item Ask supervisee to provide examples of conditioned punishment and a conditioned punisher.
\item Ask supervisee to identify examples of conditioned punishment in a client's environment.
\end{enumerate}
%
