\clearpage \section{\fourFKThirtyOne{}}
\subsection{Definition}
``The AB because of C formulation is a general statement that the relation between an event (B) and its context (A) is because of consequences (C)... Applied to Skinner's three-term contingency, the relation between (A) the setting and (B) behavior exists because of (C) consequences that occurred for previous AB (setting-behavior) relations. The idea [is] that reinforcement strengthens the setting-behavior relation rather than simply strengthening behavior'' (Moxley, 2004, p. 111).
``The three term contingency- antecedent, behavior, and consequence- is sometimes called the ABC's of behavior analysis... The term contingency has several meanings signifying various types of temporal and functional relations between behavior and antecedent and consequent variables... When a reinforcer (or punisher) is said to be contingent on a particular behavior, the behavior must be emitted for the consequence to occur'' (Cooper, Heron, \& Heward, 2007, pp. 41-42).
%
\subsection{Examples}
\begin{enumerate}
\item When John has not eaten in a while he asks his caregiver for a snack. When John asks he's given a snack. In this case the antecedents are food deprivation and the presence of someone who can provide food. The behavior would be the request for a snack and the consequence is being provided with a snack.
%
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Have supervisee identify and describe the ABC three term contingency.
\item Have supervisee give specific examples of the ABC three term contingency.
\item Have supervisee identify and describe other principles and terms related to the three term contingency (i.e., motivating operations, setting events, establishing operations, discriminative stimulus, stimulus control, etc.)
\item Have supervisee state how the ABC three term contingency related to both punishment and reinforcement.
\end{enumerate}
%
\subsection{Relevant Literature}
\begin{refsection}
\nocite{azrin1966punishment,
        cooper2007applied,
        glenn1992revolutionary,
        michael2004concepts,
        moxley2004pragmatic,
        sulzer1977applying,
        vollmer2002punishment,
        vollmer1991establishing}
\printbibliography[heading=none]
\end{refsection}
%
\subsection{Related Tasks}
\fourbOne{}\\
\foureOne{}\\
\fourgFour{}\\
\fouriOne{}\\
\fouriTwo{}\\
\fourFKTen{}\\
\fourFKEleven{}\\
\fourFKFifteen{}\\
\fourFKTwentyOne{}\\
\fourFKTwentySeven{}\\
\fourFKThirty{}\\
\fourFKThirtyThree{}\\
\fourFKThirtyFour{}\\
\fourFKThirtyFive{}\\
\fourFKFourtyOne{}\\
