%\clearpage \section[\fourgOne{}]{\fourgOne{}%
\subsection{Definition}
An important part of understanding the client you are working with is to take time to review the treatment history of this individual. There are records related to a medical history that would be beneficial to see. This would include medical procedures, medications, and any current health concerns. It's also important to get the history of treatment related to psychological/behavioral intervention as well. 

Gresham, Watson, Stewart, \& Skinner in 2001 recommend that FBAs should include a record review to understand more about the history of the client as well as information regarding previous interventions. 

Matson (2010) summarized this position by saying ``The behavior analyst should carefully review records relating to previous attempts to change potential target behaviors. Records indicating previous success with related target behaviors or a history of limited impact on a behaviour despite well-planned and faithfully implemented change programmes may be useful in selecting change targets which can be achieved within meaningful timescales'' (p. 35).

%\clearpage \section[\fourgTwo{}]{\fourgTwo{}%
\subsection{Definition}
The Behavior Analyst Certification Board (BACB) instructs that a ``behavior analyst recommends seeking a medical consultation if there is any reasonable possibility that a referred behavior influenced by medical or biological variables'' in section 3.02 Medical Consultation, of the BACB professional and ethical compliance code for behavior analysts (2014)

This is relevant both in research and practice. Therefore, the first step in the assessment process should be to determine whether the problem may be due to a medical/biological issue and whether a medical evaluation has been completed (Cooper, Heron \& Heward, 2007). Failure to rule out medical needs would be unethical as it would delay potentially necessary medical treatment that may even prove life threatening dependent on the medical concerns or the severity of the challenging behavior.

Possible pain related disorders or other medical/biological disorders that restrict an individual's ability to engage in appropriate behavior should be investigated.  Some relevant behavioral topics correlated with a high likelihood of medical and biological causes are feeding disorders, toileting challenges (e.g., encopresis and incontinence), sleep problems and self-injury. Take self-injury for example; studies have shown that self-injurious behavior (SIB) has been maintained by pain attenuation which, can be categorized as automatic negative reinforcement behavior (Carr \& Smith, 1995; O'Reilly, 1997).  In detail, an increase in painful stimulation is an establishing operation (EO), thereby increasing behavior that has been reinforced by pain reduction.

Aside from the common examples presented above, it is possible that any form of challenging behavior could be a result of an underlying medical or biological issue. For example, aggressive behavior may also be related to pain related disorders which act as an EO (Carr et al., 2003; Skinner, 1953). The argument has also been made that aggressive behavior in response to painful stimulation may be respondent behavior (Ulrich \& Azrin, 1962). Furthermore, Kennedy and Meyer (1996) found that the occurrence of allergy symptoms and sleep deprivation were correlated with an increase in escape maintained challenging behavior. 

