\subsection{Assessment}
\begin{enumerate}
\item Ask your Supervisee to identify the pros and cons of each type of preference assessment.
\item Have Supervisee memorize the authors and years for the publications of each type of preference assessment. Use flashcards to learn to fluency.
\item Have Supervisee demonstrate the use of at least 5 types of preference assessments on the job (or in a role play).
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Ask your supervisee to define a putative reinforcement assessment
\item Ask your supervisee to state the purpose of a putative reinforcement assessment
\item Require your supervisee to run a couple different types of reinforcer assessments. Provide feedback during role play and other observations.
%
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Ask your Supervisee to explain why it's important as behavior analysts to select interventions based on client preferences. 
\item Ask your Supervisee to investigate what different methods are available for evaluating clients' preferences for different interventions and report them back to you, along with advantages and disadvantages of each method.
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Have supervisee define choice and describe the matching law.
\item Have supervisee describe variables known to influence response allocation among alternatives.
\item Have supervisee set up and conduct an experiment involving concurrent schedules with different magnitudes/qualities/delays/duration of reinforcement on different options.
\item Have supervisee use the equation for the matching law to investigate matching for two different responses.
%
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Have the supervisee design a contingency contract.
\item Have the supervisee describe each component of the contract.
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Ask your supervisee to describe matching law and how it relates to choice (response allocation).
\item Have supervisee explain a situation where the matching law could be applied and describe the concurrent rates of reinforcement in place for two different behaviors.
\item Relate matching law to the selection of alternative behavior in a DRA.
%
\end{enumerate}
%
