\subsection{Assessment}
\begin{enumerate}
\item Give supervisees article abstracts on single subject research. Have them identify the dependent variable and independent variable for the study.
\item Have supervisees identify the independent and dependent variables in the example listed above.
\item Have supervisees read Horner et al., (2005) The Use of Single-Subject Research to Identify Evidence-Based Practice in Special Education and complete a brief summary of the article and ask them to identify what compromises the integrity of a functional relationship and define the quality indicators outlined for effective single-subject research.
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Ask Supervisee to list some parameters (schedule, immediacy, quality, quantity) of an independent variable that can be manipulated experimentally
\item Have supervisee describe a hypothetical parametric analysis inclusive of the independent variable parameter to be manipulated and the functional relation to be tested 
\item Ask the supervisee how they could use a parametric analysis to test for the optimal level of treatment integrity. Then discuss what parameter they would measure (i.e., schedule, immediacy) and which values they would select to answer this experimental question.  
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Ask your Supervisee to give a definition for functional relation.
\item Ask your supervisee to create other examples and a non-example of his/her own. 
\item Ask the Supervisee why it is important to only manipulate one variable at a time
\item Ask the Supervisee to state how you would know if a functional relation exists between the independent variable and the dependent variable. 
%
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Have supervisee create an NCR program and explain procedures to other supervisees.
\item Have Supervisee identify the difference between differential reinforcement and noncontingent reinforcement and give examples of both.
\item Have supervisee give examples of NCR used in his/her professional and nonprofessional life.
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Ask your Supervisee to explain why it's important as a behavior analyst to define environmental variable in observable and measurable terms. 
\item Ask your Supervisee to write an operational definition for the following independent variable:
\item Verbal Praise (Answer = (a) Immediately following the occurrence of a target behavior (temporal dimension), (b) the therapist delivered verbal praise, for example, ``great job/nice work/well done'' (verbal dimension), (c) but did not provide any physical contact such as a hi-five or pat on the back (physical dimension). The therapist was within 2 to 20 feet of the client at all times during the intervention (spatial dimension).
\end{enumerate}
%
