\clearpage \section{\fourFKThree{}}
\subsection{Definition}
Determinism - the assumption that ``the universe is a lawful and orderly place in which all phenomena occur as the result of other events'' (Cooper, Heron, \& Heward, 2007, p.5).

The implication here is that events don't just occur by accident; they occur as the result of something else happening. This is an important attitude of science because if the behavior of organisms was not orderly or lawful, scientists would be unable to identify why a behavior was occurring and therefore modify it. (Fisher, Piazza, \& Roane, 2011, p. 9) 

\subsection{Examples}
\begin{enumerate}
\item A window does not just randomly bang shut; it bangs shut because a gust of wind has blown it and this has exerted enough force upon the window to close it. 
\item A water pipe does not just spontaneously burst; it bursts because there is a fault somewhere in the system, which has caused a build up of water in the pipes, resulting in so much pressure within the system that the pipe has burst.
\item A client's self-injurious behavior does not suddenly decrease after days of high rates of SIB. It decreases because the sensory-blocking procedure gradually began to extinguish the behavior.
%
\end{enumerate}
%
\subsection{Assessment}
Ask your Supervisee to give an explanation to the scenarios below as they relate to determinism.
\begin{enumerate}
\item A glass breaks. (Possible answers could include = someone knocks it over causing it to break, the wind blows through the window and knocks it over causing it to smash, the dog kicks the glass as he runs past it, resulting in it breaking).
\item A client begins to emit correct responses when tacting the colors purple and green, which he has previously had a low rate of correct responses for. (Possible answers could include = the intervention which is in place has resulted in the appropriate stimulus control being acquired for purple and green, leading to an increased rate of correct responding; the client's Mother has been working on the colors green and purple at home with him; the client has been observing a peer tact the colors purple and green during play).
\item A client's sleep pattern changes and he begins to refuse to go to bed at 10 pm but instead will not go to bed until 3 am. (Possible answers could include = the client has been reinforced when he has been up late as his Mother has permitted him to watch TV; the client has not been woken until 4 pm in the afternoon after not going to bed until 3.30 am the night before; a client's medication has been changed and this results in disturbed sleep and periods of insomnia). 
\end{enumerate}
%
\subsection{Relevant Literature}
\begin{refsection}
\nocite{cooper2007applied,
        delprato1992some,
        fisher2014handbook}
\printbibliography[heading=none]
\end{refsection}
%
\subsection{Related Tasks}
\fourFKOne{}\\
\fourFKFour{}\\
\fourFKFive{}\\
\fourFKSix{}\\

Footnotes\\
*Please refer to 4th Ed. FK04-FK06 for a description of the other attitudes of science.\\
