\subsection{Assessment}
\begin{enumerate}
\item Ask your supervisee to come up with several examples of automatic punishment and automatic reinforcement. 
\item Ask your supervisee provide examples of how extinction of the following automatically reinforced behavior may occur: child making sounds by tapping the table, child receiving kinesthetic stimulation by flapping his arms, child throws up and eats vomit for the taste, child scratching surface for tactile stimulation on fingers, child flipping light switch on and off to gain a visual sensation
\item Ask supervisee if they will likely have to treat clients with an automatic punishment function (yes-many food refusal behavior may have an automatic punishment for example).
\end{enumerate}
%
\begin{enumerate}
\item Ask your Supervisee to identify the steps taken to shape the desired behavior of saying ``mama'' above. 
\item Ask the supervisee to identify how differential reinforcement is used to shape desired behavior.  
\item Ask your supervisee to create another example and non-example of his/her own. 
\end{enumerate}
%
\begin{enumerate}
\item Give supervisee a reinforcement program. Have him/her create a fading procedure for this program to increase the number of responses required to earn a token. 
\item Have supervisee list the five strategies for promoting generalized behavior change and have him/her give examples of each.
\item Have supervisee describe and differentiate between contrived contingencies and naturally existing contingencies and give several examples of each.
\end{enumerate}
\subsection{Assessment}
\begin{enumerate}
\item Have supervisee identify and describe the ABC three term contingency.
\item Have supervisee give specific examples of the ABC three term contingency.
\item Have supervisee identify and describe other principles and terms related to the three term contingency (i.e., motivating operations, setting events, establishing operations, discriminative stimulus, stimulus control, etc.)
\item Have supervisee state how the ABC three term contingency related to both punishment and reinforcement.
\end{enumerate}
%
