\subsection{Assessment}
\begin{enumerate}
\item Have supervisee list in order the process of completing a functional assessment.
\item Have supervisee describe the benefits and limitations of each of the assessment procedures.
\item Use behavior skills training techniques to teach your supervisee how to conduct an indirect assessment.  Accompany the supervisee in completing their first indirect assessment and provide reinforcement and feedback following the session.
\item Use behavior skills training techniques to teach your supervisee how to collect ABC data.  Explain the process, model and then practice using you tube videos of challenging behaviors.  Provide reinforcement and feedback and continue practicing until the supervisee clearly demonstrates skills in collecting ABC data.  Accompany the supervisee in completing live ABC data, take inter-rater reliability and compare scores providing reinforcement and feedback.
\item Use behavior skills training techniques to teach your supervisee how to complete an FA. Practice until the supervisee clearly demonstrates skills in the control condition and some test conditions of an FA.  Accompany the supervisee in completing live FAs, prompting and providing reinforcement and feedback.  Continue to monitor supervisee in this process until they have demonstrated the completion of multiple FA's accurately and are able to set up individualized FAs based on the descriptive data.
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Have supervisee complete a behavior rating scale on an individual based on one of their behaviors. This can include the FAST, MAS, PBQ, or another common rating scale used in behavioral assessments. Once the supervisee has completed the rating scale, have them score the form and present the results. 
\item Supervisor will create role plays in which each supervisee will collect ABC data on specific topography of problem behavior. After a number of instances have been recorded, supervisee will analyze the data and formulate a hypothesized function of the problem behavior.
\item Have supervisee read Iwata, Dorsey, Slifer, Bauman, \& Richman (1982/1994) and describe the experimental conditions of a functional analysis.
%
\end{enumerate}
%
