\clearpage \section{\fourFKTwentyFour{}}
\subsection{Definition}
Stimulus control - ``A situation in which the frequency, latency, duration, or amplitude of a behavior is altered by the presence or absence of an antecedent stimulus'' (Cooper, Heron, \& Heward, 2007, p. 705).\\

Discriminated operant - ``An operant that occurs more frequently under some antecedent conditions than under others'' (Cooper, Heron, \& Heward, 2007, p.694).\\

Discriminative stimulus (SD) - ``A stimulus in the presence of which responses of some type have been reinforced and in the absence of which the same type of responses have occurred and not been reinforced''  (Cooper, Heron, \& Heward, 2007, p. 694).

\subsection{Examples}
\begin{enumerate}
\item When the telephone rings, George picks up the receiver.  Picking up the receiver is under the stimulus control of a ringing phone. 
\item In the above example, picking up the receiver is the discriminated operant. 
\item In the above example, the telephone's ring is the discriminative stimulus.
%
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Label the following:  The traffic light turns red, John steps on the break.  What is under stimulus control? What is the discriminated operant?  What is the discriminative stimulus? 
\item Ask the supervisee to explain how he can bring a student's behavior of saying ``dog'' under the stimulus control of the picture of a dog.
\item Ask supervisee how they could use stimulus control to reduce the jumping behavior of a man who jumps up and down so much that he is damaging his feet.
%
\end{enumerate}
%
\subsection{Relevant Literature}
\begin{refsection}
\nocite{cooper2007applied}
\printbibliography[heading=none]
\end{refsection} 
%
\subsection{Related Tasks}
\fourdNineteen{}\\
\fourFKTwentyTwo{}\\
\fourFKTwentyNine{}\\
%
\clearpage \section{\fourFKTwentyFive{}}
\subsection{Definition}
The same stimulus may serve multiple functions depending on the context. For instance, an aversive stimulus can function as a positive punisher or a negative reinforcer depending on whether it is added or removed contingent on a response. An appetitive stimulus can function as a positive reinforcer or a negative punisher depending on whether it is added or removed contingent on a response.

In a behavior chain, a stimulus can function as a discriminative stimulus and a reinforcer depending on how much of the chain has been completed. Behavior chains are described by Catania as ``a sequence of discriminated operants such that responses during one stimulus are followed by other stimuli that reinforce those responses and set the occasion for the next ones'' (Catania, 2013, p. 431).

Respondent behavior interacts with operant behavior in ways that can cause a single stimulus to be an eliciting stimulus for respondent behavior as well as a discriminative stimulus for operant behavior. For example, when seeing your best friend arrive to your home for a visit, this may elicit respondent behavior one might describe as ``excitement.'' Seeing your friend may also serve as a discriminative stimulus for waving at him/her.
%
\subsection{Assessment}
\begin{enumerate}
\item Ask your supervisee to give examples of a single stimulus serving multiple functions.
\item Look at a task analysis with your supervisee. Have him/her pick a stimulus that serves as a discriminative stimulus and a reinforcer at certain parts of the performance.
%
\end{enumerate}
%
\subsection{Relevant Literature}
\begin{refsection}
\nocite{catania2013learning,
        catania1971discriminative,
        bullock2015several}
\printbibliography[heading=none]
\end{refsection}
%
\subsection{Related Tasks}
\foureOne{}\\
\fourdOne{}\\
\fourdSixteen{}\\
\fourFKFourteen{}\\
\fourFKFifteen{}\\
\fourFKSixteen{}\\
