\clearpage \section{\fouraOne{}}
\subsection{Definition}
Frequency - ``A ratio of count per observation time; often expressed as count per standard unit of time and calculated by dividing the number of responses recorded by the number of standard units of time in which observations were conducted (Cooper, Heron, \& Heward, 2007, p. 85).''*
%
\subsection{Examples}
\begin{enumerate}
\item Hand Raising - A student is sitting in an hour long class. The student raises his hand 3 times to ask and answer questions during the class. The bell rings once and the student goes to his next class. Frequency of hand raising is 3 per hour.
\end{enumerate}
% 
\subsection{Assessment} 
\begin{enumerate}
\item Ask your supervisee to identify the frequency of hand raising above.
\item Ask your supervisee to create another example and non-example of his/her own.
\item Have supervisee measure a frequency of a behavior on the job or in a role play.
\item Have supervisee graph the frequency measured on the job or in a role play.
\end{enumerate}
%
\subsection{Relevant Literature}
\begin{refsection}
\nocite{catania2013learning,cooper2007applied}
\printbibliography[heading=none]
\end{refsection}

\subsection{Related Tasks} 
\fouriOne{}\\
\fourhOne{}\\
\fourFKFourtySeven{}\\
%
\subsection{Footnotes}
* Alternatively, frequency is not always defined synonymously with rate throughout the discipline of behavior analysis. Catania (2013, p. 443) defines frequency as ``total responses over a fixed time, over a session of variable duration or, in trial procedure, over a fixed number of trials.'' Cooper, Heron, \& Heward (2007) functionally defines ``count'' as Catania defines ``frequency.''
