\clearpage \section[\fourkEight{}]{\fourkEight{}%
              \sectionmark{K-08 Establish support...}}
\sectionmark{K-08 Establish support...}
\subsection{Definition}
As a behavior analyst, it is important to conduct yourself with professionalism to your clients and their family and also to individuals from other disciplines that may support your client.  You must enlist a circle of care around your client, which will help you to better understand your client through the lenses of another discipline.  For example if you have a child who has feeding refusal, taking the time to enlist information from the nutritionist, speech pathologist, doctors and occupational therapists will help you to provide safe and effective treatment.

In addition, when providing treatment having help from people within the client's family, the community, and from the circle of care around your client will enable you to generalize skills to new environments, new people and new activities.  These individuals can be a great asset in troubleshooting and providing additional data as well.

Additionally, when your goals are met, you will leave.  In order for the continued support of your client and the maintenance of the goals, it is important to enlist individuals who will be with the client for a longer period.

Bailey and Burch (2010) provide a useful book on professional strategies. He provides several suggestions on how to establish a working relationship in the best interest of the client.  Establishing yourself as a positive reinforcer for your colleagues by demonstrating integrity, basic meeting etiquette, providing a professional image, using nontechnical language, listening to others, and bringing their opinions into the assessment. 
%
\subsection{Assessment}
\begin{enumerate}
\item Ask supervisee to describe the importance of enlisting the help of direct and indirect consumers.
\item Use behavior skill tracking to teach and practice describing interventions in nontechnical terms.
\item Discuss challenges in dealing with colleagues within different fields and strategies to help.
\end{enumerate}
%
\subsection{Relevant Literature}
\begin{refsection}
\nocite{bailey201025,
        bailey2013ethics,
        bac2014professional}
\printbibliography[heading=none]
\end{refsection} 
%                         
\subsection{Related Tasks}
\fourgSeven{}\\
\fourkNine{}\\
\fourkTen{}\\
