\subsection{Assessment}
\begin{enumerate}
\item Have your supervisee list and describe applicable antecedent interventions.
\item In a clinical setting or during role-play, have your supervisee describe what motivating operations may be affecting the client's behavior.
\item Describe a scenario and have the supervisee lists some potential antecedent strategies that can be used and have them describe why they chose these strategies.
\end{enumerate}
%
%\subsection{Assessment}
\begin{enumerate}
\item Have supervisee identify at least 7 unconditioned motivating operations. Have him/her describe their reinforcer-establishing effect as well as their evocative effect. (see page 379, table 16.1 in Cooper et al., 2007)
\item Have supervisee identify UMOs that decrease reinforcer effectiveness and abate relevant behavior. Have him/her describe the reinforcer-abolishing effect and the abative effect of each UMO. (See page 380, table 16.2 in Cooper et al., 2007).
\item Have supervisee explain how to weaken the effects of a UMO. (See page 380-381 in Cooper et al., 2007).
\item Have supervisee explain the difference between motivating operations and discriminative stimuli. (See page 377 in Cooper et al., 2007).
%
\end{enumerate}
%
%\subsection{Assessment}
\begin{enumerate}
\item Have supervisee describe the three types of CMOs. Have him/her give examples of each. 
\item Have supervisee explain the definitions for conditioned and unconditioned motivating operations in simple terms that someone who does not have ABA experience can understand.
\item Have supervisee explain how to weaken the effects of each of the three types of CMO. 
%
\end{enumerate}
%
%\subsection{Assessment}
\begin{enumerate}
\item Have supervisee list and define the 3 types of conditioned motivating operations. 
\item Have him/her give examples of each type of conditioned motivating operation.
\item Have supervisee explain the difference between conditioned and unconditioned motivating operations.
%
\end{enumerate}
%
%\subsection{Assessment}
\begin{enumerate}
\item Have supervisee explain the difference between SD s and MOs.
\item Have the supervisee to create additional examples of SD s and MOs.
\item Provide the supervisee with examples of responses and the reinforcers for those responses. Have the supervisee describe potential ways to increase and decrease the value of the reinforcer.
\end{enumerate}
%
%\subsection{Assessment}
\begin{enumerate}
\item Ask supervisee to define MOs and explain the basic characteristics.
\item Ask supervisee to discriminate between behavior-altering effects and repertoire-altering effects.
\item Ask supervisee to identify potential MOs for client's behavior.
\item Ask supervisee to provide examples of behavior-altering effects and repertoire-altering effects that are operating in a client's environment.
\end{enumerate}
%
