\clearpage \section[\fourkFive{}]{\fourkFive{}%
              \sectionmark{K-05 Design and use systems...}}
\sectionmark{K-05 Design and use systems...}
\subsection{Definition}
Procedural Integrity - ``The extent to which the independent variable is applied exactly as planned and described and no other unplanned variables are administered inadvertently along with the planned treatment'' (Cooper Heron, \& Heward, 2007, pp. 706-707).

Treatment Drift - ``An undesirable situation in which the independent variable of an experiment is applied differently during later stages than it was at the outset of the study'' (Cooper Heron, \& Heward, 2007, p. 706).

Low treatment integrity is not only bad for research (confounding, cannot interpret the results) but can also lead to inconsistencies and poor outcomes in treatments.  These can be related to many factors such as experimenter bias (unfair advantage to see positive results), staff implementing only procedures they favor, treatment too difficult to implement, poor staff training, or staff turnover.

Systems to Avoid Treatment Drift
\begin{enumerate}
\item Precise operational definition
\item Make behavioral plan simple and easy to administer
\item Provide competency-based training (use behavior skills training)
\item Assess treatment integrity
\end{enumerate}

Assessing Treatment Integrity
\begin{enumerate}
\item Provide a brief checklist of each of the components in the treatment plan
\item May be self-monitored but important to conduct inter-rater reliability
\item Establish a schedule to complete the treatment integrity
\item Graph the percent of treatment integrity and monitor to ensure treatment drift does not occur
\end{enumerate}
%
\subsection{Assessment}
\begin{enumerate}
\item Ask supervisee to describe why procedural integrity is important.
\item Ask supervisee to create a procedural integrity checklist for a behavioral program.
\item Ask supervisee to collect data using the procedural integrity checklist in the natural environment and take inter-rater reliability measurement with yourself, discuss discrepancies, repeat if necessary.
\end{enumerate}
%
\subsection{Relevant Literature}
\begin{refsection}
\nocite{cooper2007applied,
        johnston2010strategies,
        wolery1994procedural}
\printbibliography[heading=none]
\end{refsection} 
%                         
\subsection{Related Tasks}
\fourfOne{}\\
\fourhThree{}\\
\fourhFour{}\\
\fourkThree{}\\
\fourkFour{}\\
%
\subsection{Footnotes}
Also called procedural fidelity, treatment integrity, procedural reliability, or treatment adherence.
